\documentclass[10pt]{article}
\usepackage[top=.2in, bottom=.2in, left=.2in, right=.4in]{geometry}
\setlength{\tabcolsep}{0in}
\begin{document}
\textbf{\LARGE Daniel Cox}
  \begin{center}
    \begin{tabular*}{7.5in}{l@{\extracolsep{0.05in}}l@{\extracolsep{1in}}l}
      &http://danielpcox.com     & Current Address: \\
      &danielpcox@gmail.com      &            3100 Saint Paul St. \#213    \\
      &412.532.6269                &              Baltimore, MD 21218\\ \\
    \end{tabular*}
  \end{center}

  {\large \textbf{Objective}}

  \begin{flushleft}
    \addtolength{\leftskip}{.3in}
    A position in applied computer science research with a company seeking a
    record of superior innovation and accuracy in analysis, as well as leadership
    in its field, and a lasting, positive impact on society.
  \end{flushleft}

  {\large \textbf{Education}}

  \begin{flushleft}
    \addtolength{\leftskip}{.3in}
        \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
            \textbf{Cornell University}, Bachelors of Science Computer Science & 08/2007 - 05/2011 \\
            Cumulative GPA: 3.27
        \end{tabular*}
  \end{flushleft}

  {\large \textbf{Relevant Coursework}}

  \begin{flushleft}
    \addtolength{\leftskip}{.3in}
    Analysis of Algorithms, Operating Systems, Introduction to Analysis of Algorithms, Systems Programming,
    Introduction to Natural Language Processing, Introduction to Cognitive Science, Foundations of Artificial Intelligence,
    Practicum in AI, Introduction to Database Systems, Networks, Discrete Structures, Data Structures and Functional Programming,
    Introduction to Digital Logic Design, Object-Oriented Programming and Data Structures, Introduction to Computer Game Design,
    Information Systems and Analysis, Computational Methods for Management and Economics, Prove It (mathematical proof course).
  \end{flushleft}

  {\large \textbf{Technologies}}

  \begin{flushleft}
    \addtolength{\leftskip}{.3in} 
    Linux server administration and related technologies, Test-Driven Development, Continuous Integration,
    C, C\#, Java, Ruby (and Rails), Python, Perl, R, MATLAB, OCaml, PHP, XHTML, CSS, Javascript, jQuery, Git, Subversion, MySQL and \LaTeX.
  \end{flushleft}

  {\large \textbf{Experience}}

  \begin{itemize}
    \item
    \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
      \textbf{Web Application Programming Intern}, Desiring God, Minneapolis, MN & Summer 2008/2009/2010\\
    \end{tabular*}
    \begin{itemize}
      \item Collaborated with wide range of skill sets to port entire company website to Ruby on Rails, now live at desiringgod.org.
      \item Contributed to the database architecture and site planning, and developed significant portions of the (Ruby on Rails) back-end of the site.
    \end{itemize}

    \item
    \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
      \textbf{Emergency Medical Technician}, BI Ambulance Association, Bainbridge Island, WA & 06-08/2007\\
    \end{tabular*}
    \begin{itemize}
      \item Formerly Certified Washington State EMT-B
      \item Worked for private ambulance company BIAA caring for and transporting patients in emergency situations.
      \item Work required well-developed interpersonal, diagnostics and treatment skills in dealing with all personality types in distress.
    \end{itemize}

    \item
    \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
      \textbf{Server Devel. and Reports Programming Intern}, eAcceleration Corp., Poulsbo, WA & 07/2004-10/2006\\
    \end{tabular*}
    \begin{itemize}
      \item Wrote dashboards and developed reports scripts for company databases and migrated old reports scripts to current technologies.
      \item Evaluated new technologies (such as Ruby on Rails) for potential future migration, reported findings to management.
    \end{itemize}

    \item
    \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
      \textbf{Web Application Programmer}, What's For Dinner Kitchen, Poulsbo, WA & 06-09/2006\\
    \end{tabular*}
    \begin{itemize}
      \item Contracted alone for four months to design and build the ecommerce website of a startup meal-preparation business.
      \item Worked closely with the owner at every stage of the process, including maintenance for some time after.
    \end{itemize}

  \end{itemize}

  {\large \textbf{Extra Curricular}}

  \begin{itemize}
    \item Active member and organizer of Cornell's chapter of Campus Crusade for Christ before graduation. Built cornellcru.com, trained a group of underclassmen to replace me, mentored several younger students.
    \item Swing dance with Rooftop Mayhem and CU Swing, performed and tutored at events.
  \end{itemize}

\end{document}
